Incentivizing Exploration with Unbiased History

### 2018-11-01 app-warmup.tex
ct,cm->N0,C0

\section{Proofs from Section~\ref{sec:warmup}}
\label{app:warmup}

\begin{proof}[Proof of Lemma~\ref{lem:greedy}]
  Fix any arm $a$. Let $\GdT = (K-1) \cdot c_T + 1$ and
  $\GdP = (1/3)^{\GdT}$. \swedit{We will condition on the event that
    all the realized rewards in $\GdT$ rounds are 0, which occurs with
    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.}
  In this case, we want to show that arm $a$ is pulled at least
  once. We prove this by contradiction. Suppose arm $a$ is not pulled. By
  the pigeonhole principle, we know that there is some other arm $a'$
  that is pulled at least $c_T + 1$ rounds. Let $t$ be the round in
  which arm $a'$ is pulled exactly $c_T + 1$ times. By Assumption
  \ref{ass:embehave}, we know
  \[
    \hat{\mu}_{a'}^t \leq 0 + c_m / \sqrt{c_T} < 1/3.
  \]
  \nicomment{Wait, where did we set $c_T$?} On the other hand, we have
  $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
  the fact that in round $t$, arm $a'$ is pulled, instead of arm $a$.
  \swdelete{ In addition, we know that this case happens with
    probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is
    at most $2/3$. To sum up, we know that with probability at least
    $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.}
   \jmcomment{Agree with these changes.}
\end{proof}

@@

For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
\[
|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}.
\]
By $W_1$ and Assumption \ref{ass:embehave}, we have
\[
|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{\fdpN T_1/2}}.
\]
Therefore,
\[
|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}+\frac{c_m}{\sqrt{\fdpN T_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.
\OMIT{Notice that if we know the gap parameter is known to be larger than
$\Delta$, we can set
\[
T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
\]
In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
\]
This completes the proof.}
\end{proof}

>>>>

%!TEX root = main.tex
\section{Proofs from Section~\ref{sec:warmup}}
\label{app:warmup}

\begin{proof}[Proof of Lemma~\ref{lem:greedy}]
  Fix any arm $a$. Let $\GdT = (K-1) \cdot N_0 + 1$ and
  $\GdP = (1/3)^{\GdT}$. \swedit{We will condition on the event that
    all the realized rewards in $\GdT$ rounds are 0, which occurs with
    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.}
  In this case, we want to show that arm $a$ is pulled at least
  once. We prove this by contradiction. Suppose arm $a$ is not pulled. By
  the pigeonhole principle, we know that there is some other arm $a'$
  that is pulled at least $N_0 + 1$ rounds. Let $t$ be the round in
  which arm $a'$ is pulled exactly $N_0 + 1$ times. By Assumption
  \ref{ass:embehave}, we know
  \[
    \hat{\mu}_{a'}^t \leq 0 + C_0 / \sqrt{N_0} < 1/3.
  \]
  \nicomment{Wait, where did we set $N_0$?} On the other hand, we have
  $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
  the fact that in round $t$, arm $a'$ is pulled, instead of arm $a$.
  \swdelete{ In addition, we know that this case happens with
    probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is
    at most $2/3$. To sum up, we know that with probability at least
    $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.}
   \jmcomment{Agree with these changes.}
\end{proof}

@@

For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
\[
|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}.
\]
By $W_1$ and Assumption \ref{ass:embehave}, we have
\[
|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{C_0}{\sqrt{\fdpN T_1/2}}.
\]
Therefore,
\[
|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}+\frac{C_0}{\sqrt{\fdpN T_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.
\OMIT{Notice that if we know the gap parameter is known to be larger than
$\Delta$, we can set
\[
T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
\]
In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
\]
This completes the proof.}
\end{proof}

### 2018-11-01 llevel.tex
information graph -> info-graph
ct,cm->N0,C0

Finally we define the information flow. Agents in the first level only observe the history defined in the \ALGG run. For agents in group $G_{l,u,v}$ with $l\geq 2$, they observe all the history in the first $l-2$ levels (both $G$-groups and $\Gamma$-groups) and history in group $G_{l-1,v,w}$ for all $w \in [S]$. Agents in group $\Gamma_{l,u,v}$ observe the same history as agents in group $G_{l,u,v}$.

@@

We prove the above via induction on $l$. %For notation convenience, define $\bar{\mu}^{l,u}_a$  to be the empirical mean of arm $a$ pulls in the history observed by agents in groups $G_{l,1,u},...,G_{l,S,u}$ and $\Gamma_{l,1,u},...,\Gamma_{l,S,u}$ (they observe the same history).
We start by the base case when $l=2$. For each arm $a$, $W_4$ implies there exists $u_a$ such that $W^{u_a,a,high}_4$ and $W^{u_a,3-a,low}_4$ happen. For an agent $t$  in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$.
$W_4^{u_a,a,high}$,  $W_1^{a,u_a,v}$ and $W_2$ together imply that 
\begin{align*}
\bar{\mu}_a ^t &\geq \mu_a + \left(\fdpN T_1S \cdot \frac{1}{\sqrt{\fdpN T_1S}} - \GdT \sqrt{T_1\log(T)} S\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}S}} \right) \cdot \frac{1}{(\fdpN T_1+ \GdT \sqrt{T_1\log(T)})S} \\
&> \mu_a + \frac{1}{4\sqrt{\fdpN T_1S}}.
\end{align*}
The second last inequality holds when $T$ is larger than some constant.
Similarly, we also have
\[
\bar{\mu}_{3-a}^t< \mu_{3-a}   - \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}.
\]
Then we have
\begin{align*}
\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a} + \frac{1}{4\sqrt{\fdpN T_1S}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}\\
&\geq -\varepsilon_1+ \frac{1}{4\sqrt{\fdpN T_1S}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}\\
&\geq \frac{1}{8\sqrt{\fdpN T_1S}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1S}}.
\end{align*}
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{c_m}{\sqrt{\fdpN T_1S/2}} - \frac{c_m}{\sqrt{\fdpN[3-a] T_1S/2}}\\
&> \frac{1}{8\sqrt{\fdpN T_1S}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1S}} -   \frac{c_m}{\sqrt{\fdpN T_1S/2}} - \frac{c_m}{\sqrt{\fdpN[3-a] T_1S/2}}\\
&>0.
\end{align*}
The last inequality holds since $c_m$ is a small enough constant defined in Assumption \ref{ass:embehave}. Therefore we know agents in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$ all pull arm $a$.

Now we consider the case when $l > 2$ and assume the claim is true for smaller $l$'s. For each arm $a$, $W_3$ implies that there exists $u_a$ such that $W^{l-1,u_a,a,high}_3$ and $W^{l-1,u_a,3-a,low}_3$ happen. Recall $n^{l-1,u_a,a}$ is the number of arm $a$ pulls in groups $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$. The induction hypothesis implies that $n^{l-1,u_a,a} \geq T_{l-1}$. $W^{l-1,u_a,a,high}_3$ together with $n^{l-1,u_a,a} \geq T_{l-1}$ implies that the empirical mean of arm $a$ pulls in group $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$ is at least $\mu_a + 1/\sqrt{n^{l-1,u_a,a}}$. For any agent $t$ in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$, it observes history of groups $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$ and all groups in levels below level $l-1$. Notice that the groups in the first $l-2$ levels have at most $(T_1 \GdT + T_2 + \cdots +T_{l-2})S^3 \leq T_{l-1}/(12\log(T)) \leq n^{l-1,u_a,a}/(12\log(T))$ agents. By $W_2$, we have
\begin{align*}
\bar{\mu}_a ^t &\geq \mu_a + \left(n^{l-1,u_a,a}  \cdot \frac{1}{\sqrt{n^{l-1,u_a,a} }}- (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3\cdot \sqrt{\frac{3\log(T)}{ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3}} \right) \\
&~~~\cdot \frac{1}{n^{l-1,u_a,a}+ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3} \\
&> \mu_a + \frac{1}{4\sqrt{n^{l-1,u_a,a}  }}.
\end{align*}
The third last inequality holds when $T$ larger than some constant.
Similarly, we also have
\[
\bar{\mu}_{3-a}^t < \mu_{3-a}   -\frac{1}{4\sqrt{n^{l-1,u_a,3-a}  }}.
\]
Then we have
\begin{align*}
\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a}+ \frac{1}{4\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{4\sqrt{n^{l-1,u_a,3-a}  }}\\
&\geq -\varepsilon_{l-1}+ \frac{1}{4\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{4\sqrt{n^{l-1,u_a,3-a}  }}\\
&\geq \frac{1}{8\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{8\sqrt{n^{l-1,u_a,3-a}  }}.
\end{align*}
The last inequality holds because $n^{l-1,u_a,a}$ and $n^{l-1,u_a,3-a}$ are at most $T_{l-1} S$. By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{c_m}{\sqrt{n^{l-1,u_a,a} }} - \frac{c_m}{\sqrt{n^{l-1,u_a,3-a}}}\\
&> \frac{1}{8\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{8\sqrt{n^{l-1,u_a,3-a}  }} -  \frac{c_m}{\sqrt{n^{l-1,u_a,a} }} - \frac{c_m}{\sqrt{n^{l-1,u_a,3-a}}}\\
&>0.
\end{align*}
The last inequality holds since $c_m$ is a small enough constant defined in Assumption \ref{ass:embehave}.
Therefore agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$.
\end{proof}

@@

\begin{itemize}
\item $\varepsilon_{l-1} S \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l = 2$(i.e. $\varepsilon_1S\leq \mu_1 - \mu_2 \leq \varepsilon_0$): We know agents in level at least 2 will observe at least $\fdpN T_1/2$ pulls of arm $a$ for $a \in \{1,2\}$. By $W_2$, for any agent in level at least 2, we have
\[
|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S\fdpN T_1/2}}.
\]
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
&\geq \mu_1 -\mu_2-\sqrt{\frac{3\log(T)}{S\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{S\fdpN[2]T_1/2}}- \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
&\geq\frac{\sqrt{S}}{4\sqrt{\fdpN[1]T_1}} +  \frac{\sqrt{S}}{4\sqrt{\fdpN[2]T_1}}-\sqrt{\frac{3\log(T)}{S\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{S\fdpN[2]T_1/2}}- \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
&>0.
\end{align*}
Therefore agents in level at least 2 will all pull arm 1.

\item $\varepsilon_{l-1} S \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l > 2$: By claim \ref{clm:l2_explore}, for any agent $t$ in level at least $l$, that agent will observe at least $T_{l-1}$ arm $a$ pulls. By $W_2$, we have
\[
|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{T_{l-1}}}.
\]
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2c_m}{\sqrt{T_{l-1}}} \\
&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2c_m}{\sqrt{T_{l-1}}} \\
&\geq\sqrt{\frac{S}{16T_{l-1}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2c_m}{\sqrt{T_{l-1}}} \\
&>0.
\end{align*}
Therefore agents in level at least $l$ will all pull arm 1.

\item $\varepsilon_{l-2} < \mu_1 - \mu_2 < \varepsilon_{l-2}S$ for $l =3$ (i.e. $\varepsilon_1 < \mu_1 - \mu_2 < \varepsilon_1S$): By Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $3$, that agent will observe at least $T_1\fdpN S^2/2$ arm $a$ pulls (just from the first level). By $W_2$, we have
\[
|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S^2\fdpN T_1/2}}.
\]
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{c_m}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{c_m}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
&\geq \mu_1 -\mu_2 -  \sqrt{\frac{3\log(T)}{S^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{S^2\fdpN[2]T_1/2}}- \frac{c_m}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{c_m}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
&\geq\frac{1}{4\sqrt{S\fdpN[1]T_1}} + \frac{1}{4\sqrt{S\fdpN[2]T_1}}  -  \sqrt{\frac{3\log(T)}{S^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{S^2\fdpN[2]T_1/2}}- \frac{c_m}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{c_m}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
&>0.
\end{align*}
Therefore agents in level at least 3 will all pull arm 1.

\item $\varepsilon_{l-2} < \mu_1 - \mu_2 < \varepsilon_{l-2}S$ for $l >3$: Since $\mu_1-\mu_2 < \varepsilon_{l-2}S < \varepsilon_{l-3}$, by Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $l$, that agent will observe at least $T_{l-2}S^2$ arm $a$ pulls (just from level $l-2$). By $W_2$, we have
\[
|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S^2T_{l-2}}}.
\]
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2c_m}{\sqrt{S^2T_{l-2}}} \\
&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{S^2T_{l-2}}}- \frac{2c_m}{\sqrt{S^2T_{l-2}}} \\
&\geq\frac{1}{4\sqrt{ST_{l-2}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2c_m}{\sqrt{T_{l-1}}} \\
&>0.
\end{align*}
Therefore agents in level at least $l$ will all pull arm 1. 
\end{itemize}
\end{proof}

>>>>

Finally we define the info-graph. Agents in the first level only observe the history defined in the \ALGG run. For agents in group $G_{l,u,v}$ with $l\geq 2$, they observe all the history in the first $l-2$ levels (both $G$-groups and $\Gamma$-groups) and history in group $G_{l-1,v,w}$ for all $w \in [S]$. Agents in group $\Gamma_{l,u,v}$ observe the same history as agents in group $G_{l,u,v}$.

@@

We prove the above via induction on $l$. %For notation convenience, define $\bar{\mu}^{l,u}_a$  to be the empirical mean of arm $a$ pulls in the history observed by agents in groups $G_{l,1,u},...,G_{l,S,u}$ and $\Gamma_{l,1,u},...,\Gamma_{l,S,u}$ (they observe the same history).
We start by the base case when $l=2$. For each arm $a$, $W_4$ implies there exists $u_a$ such that $W^{u_a,a,high}_4$ and $W^{u_a,3-a,low}_4$ happen. For an agent $t$  in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$.
$W_4^{u_a,a,high}$,  $W_1^{a,u_a,v}$ and $W_2$ together imply that 
\begin{align*}
\bar{\mu}_a ^t &\geq \mu_a + \left(\fdpN T_1S \cdot \frac{1}{\sqrt{\fdpN T_1S}} - \GdT \sqrt{T_1\log(T)} S\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}S}} \right) \cdot \frac{1}{(\fdpN T_1+ \GdT \sqrt{T_1\log(T)})S} \\
&> \mu_a + \frac{1}{4\sqrt{\fdpN T_1S}}.
\end{align*}
The second last inequality holds when $T$ is larger than some constant.
Similarly, we also have
\[
\bar{\mu}_{3-a}^t< \mu_{3-a}   - \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}.
\]
Then we have
\begin{align*}
\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a} + \frac{1}{4\sqrt{\fdpN T_1S}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}\\
&\geq -\varepsilon_1+ \frac{1}{4\sqrt{\fdpN T_1S}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}\\
&\geq \frac{1}{8\sqrt{\fdpN T_1S}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1S}}.
\end{align*}
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{C_0}{\sqrt{\fdpN T_1S/2}} - \frac{C_0}{\sqrt{\fdpN[3-a] T_1S/2}}\\
&> \frac{1}{8\sqrt{\fdpN T_1S}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1S}} -   \frac{C_0}{\sqrt{\fdpN T_1S/2}} - \frac{C_0}{\sqrt{\fdpN[3-a] T_1S/2}}\\
&>0.
\end{align*}
The last inequality holds since $C_0$ is a small enough constant defined in Assumption \ref{ass:embehave}. Therefore we know agents in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$ all pull arm $a$.

Now we consider the case when $l > 2$ and assume the claim is true for smaller $l$'s. For each arm $a$, $W_3$ implies that there exists $u_a$ such that $W^{l-1,u_a,a,high}_3$ and $W^{l-1,u_a,3-a,low}_3$ happen. Recall $n^{l-1,u_a,a}$ is the number of arm $a$ pulls in groups $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$. The induction hypothesis implies that $n^{l-1,u_a,a} \geq T_{l-1}$. $W^{l-1,u_a,a,high}_3$ together with $n^{l-1,u_a,a} \geq T_{l-1}$ implies that the empirical mean of arm $a$ pulls in group $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$ is at least $\mu_a + 1/\sqrt{n^{l-1,u_a,a}}$. For any agent $t$ in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$, it observes history of groups $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$ and all groups in levels below level $l-1$. Notice that the groups in the first $l-2$ levels have at most $(T_1 \GdT + T_2 + \cdots +T_{l-2})S^3 \leq T_{l-1}/(12\log(T)) \leq n^{l-1,u_a,a}/(12\log(T))$ agents. By $W_2$, we have
\begin{align*}
\bar{\mu}_a ^t &\geq \mu_a + \left(n^{l-1,u_a,a}  \cdot \frac{1}{\sqrt{n^{l-1,u_a,a} }}- (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3\cdot \sqrt{\frac{3\log(T)}{ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3}} \right) \\
&~~~\cdot \frac{1}{n^{l-1,u_a,a}+ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3} \\
&> \mu_a + \frac{1}{4\sqrt{n^{l-1,u_a,a}  }}.
\end{align*}
The third last inequality holds when $T$ larger than some constant.
Similarly, we also have
\[
\bar{\mu}_{3-a}^t < \mu_{3-a}   -\frac{1}{4\sqrt{n^{l-1,u_a,3-a}  }}.
\]
Then we have
\begin{align*}
\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a}+ \frac{1}{4\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{4\sqrt{n^{l-1,u_a,3-a}  }}\\
&\geq -\varepsilon_{l-1}+ \frac{1}{4\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{4\sqrt{n^{l-1,u_a,3-a}  }}\\
&\geq \frac{1}{8\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{8\sqrt{n^{l-1,u_a,3-a}  }}.
\end{align*}
The last inequality holds because $n^{l-1,u_a,a}$ and $n^{l-1,u_a,3-a}$ are at most $T_{l-1} S$. By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{C_0}{\sqrt{n^{l-1,u_a,a} }} - \frac{C_0}{\sqrt{n^{l-1,u_a,3-a}}}\\
&> \frac{1}{8\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{8\sqrt{n^{l-1,u_a,3-a}  }} -  \frac{C_0}{\sqrt{n^{l-1,u_a,a} }} - \frac{C_0}{\sqrt{n^{l-1,u_a,3-a}}}\\
&>0.
\end{align*}
The last inequality holds since $C_0$ is a small enough constant defined in Assumption \ref{ass:embehave}.
Therefore agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$.
\end{proof}

@@

\begin{itemize}
\item $\varepsilon_{l-1} S \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l = 2$(i.e. $\varepsilon_1S\leq \mu_1 - \mu_2 \leq \varepsilon_0$): We know agents in level at least 2 will observe at least $\fdpN T_1/2$ pulls of arm $a$ for $a \in \{1,2\}$. By $W_2$, for any agent in level at least 2, we have
\[
|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S\fdpN T_1/2}}.
\]
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{C_0}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{C_0}{\sqrt{S\fdpN[2]T_1/2}}\\
&\geq \mu_1 -\mu_2-\sqrt{\frac{3\log(T)}{S\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{S\fdpN[2]T_1/2}}- \frac{C_0}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{C_0}{\sqrt{S\fdpN[2]T_1/2}}\\
&\geq\frac{\sqrt{S}}{4\sqrt{\fdpN[1]T_1}} +  \frac{\sqrt{S}}{4\sqrt{\fdpN[2]T_1}}-\sqrt{\frac{3\log(T)}{S\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{S\fdpN[2]T_1/2}}- \frac{C_0}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{C_0}{\sqrt{S\fdpN[2]T_1/2}}\\
&>0.
\end{align*}
Therefore agents in level at least 2 will all pull arm 1.

\item $\varepsilon_{l-1} S \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l > 2$: By claim \ref{clm:l2_explore}, for any agent $t$ in level at least $l$, that agent will observe at least $T_{l-1}$ arm $a$ pulls. By $W_2$, we have
\[
|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{T_{l-1}}}.
\]
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2C_0}{\sqrt{T_{l-1}}} \\
&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2C_0}{\sqrt{T_{l-1}}} \\
&\geq\sqrt{\frac{S}{16T_{l-1}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2C_0}{\sqrt{T_{l-1}}} \\
&>0.
\end{align*}
Therefore agents in level at least $l$ will all pull arm 1.

\item $\varepsilon_{l-2} < \mu_1 - \mu_2 < \varepsilon_{l-2}S$ for $l =3$ (i.e. $\varepsilon_1 < \mu_1 - \mu_2 < \varepsilon_1S$): By Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $3$, that agent will observe at least $T_1\fdpN S^2/2$ arm $a$ pulls (just from the first level). By $W_2$, we have
\[
|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S^2\fdpN T_1/2}}.
\]
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{C_0}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{C_0}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
&\geq \mu_1 -\mu_2 -  \sqrt{\frac{3\log(T)}{S^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{S^2\fdpN[2]T_1/2}}- \frac{C_0}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{C_0}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
&\geq\frac{1}{4\sqrt{S\fdpN[1]T_1}} + \frac{1}{4\sqrt{S\fdpN[2]T_1}}  -  \sqrt{\frac{3\log(T)}{S^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{S^2\fdpN[2]T_1/2}}- \frac{C_0}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{C_0}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
&>0.
\end{align*}
Therefore agents in level at least 3 will all pull arm 1.

\item $\varepsilon_{l-2} < \mu_1 - \mu_2 < \varepsilon_{l-2}S$ for $l >3$: Since $\mu_1-\mu_2 < \varepsilon_{l-2}S < \varepsilon_{l-3}$, by Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $l$, that agent will observe at least $T_{l-2}S^2$ arm $a$ pulls (just from level $l-2$). By $W_2$, we have
\[
|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S^2T_{l-2}}}.
\]
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2C_0}{\sqrt{S^2T_{l-2}}} \\
&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{S^2T_{l-2}}}- \frac{2C_0}{\sqrt{S^2T_{l-2}}} \\
&\geq\frac{1}{4\sqrt{ST_{l-2}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2C_0}{\sqrt{T_{l-1}}} \\
&>0.
\end{align*}
Therefore agents in level at least $l$ will all pull arm 1. 
\end{itemize}
\end{proof}
